Big Ideas in Sports Analytics and Statistical Tools for their Investigation

### 2022-06-01 sports_analytics.Rmd
BTM

A popular method for estimating team strength in sports is through pairwise evaluations. Perhaps the most famous probability model for predicting the outcome of a paired comparison is the Bradley-Terry model (BTM) [@Bradley1952]. For a pair of players (or teams) $i$ and $j$, let $\Pi_{ij}$ denote the probability that $i$ is preferred to $j$. Then the BTM is a logistic regression model with parameters $\{\beta_i\}$ such that

@@

Here, $exp(\beta_i)$ is often viewed as a representation of player $i$'s ability. The BTM can be implemented in `R` [@Rcitation2022] via the \pkg{BradleyTerry2} package [@R-BradleyTerry2].

>>>>

A popular method for estimating team strength in sports is through pairwise evaluations. Perhaps the most famous probability model for predicting the outcome of a paired comparison is the Bradley-Terry model (BTM) [@Bradley1952]. For a pair of players (or teams) $i$ and $j$, let $\Pi_{ij}$ denote the probability that $i$ is preferred to $j$. Then the BTM is a logistic regression model with parameters $\beta_i, \beta_j$ such that

@@

Here, $\exp{\beta_i}$ is often viewed as a representation of player $i$'s ability. The BTM can be implemented in `R` [@Rcitation2022] via the \pkg{BradleyTerry2} package [@R-BradleyTerry2].

For example, ...

```{r btm, echo=TRUE}
library(Lahman)
library(BradleyTerry2)
# show BTM for Pirates vs. Yankees in 1960
# or Red Sox vs. Yankees in 2003/2004
```
